Mapping the characteristics of small-scale agricultural systems at national extents using small sat data and an active learning approach

### 2021-02-25 inst/manuscript/manuscript.Rmd
Discussion updated through penultimate section

Based on this reference sample, we found that the overall accuracy of the pixel-wise classifications was 88% (Table \href{tab:mapaccuracy}). This overall level of accuracy varied within four smaller zones (Figure S9A), ranging from 83.3% in Zone 1 (comprised of AOIs 1-3) to 93.6% in Zone 3 (AOIs 10, 11, 13, 15, and 16). Examining the accuracies of the individual classes, the Producer's accuracy of the cropland class was 61.7% across Ghana, ranging from 45.6% in Zone 3 to 67.9% in Zone 1. The User's accuracy for cropland was 67.3% overall, ranging from 59.8% in Zone 4 to 71.2% in Zone 1. Both measures of accuracy were substantially higher for the non-cropland class across all zones, typically exceeding 90%, with the lowest accuracies for this class found in Zone 1 (Producer's = 89.3% and User's = 87.7%, respectively).

The overall accuracies obtained from the segmented maps were generally 1-2 percentage points lower than those of the per-pixel maps, while User's accuracies tended to be 8-10 percentage points less (Table \href{tab:mapaccuracy}). In contrast, Producer's accuracies were 15-20 points higher than in the per-pixel map, indicating that the segmentation step helped reduce omission error, but substantially increased false positive errors.

@@

cap <- glue::glue("The average size and total number of crop fields for each ", 
                  "AOI and for Ghana overall. The original and bias-adjusted values", 
                  " for each measure are provided, as well as the total number", 
                  " of 0.05$^\\circ$ degree tiles in each AOI.")
knitr::kable(size_n_tab, format = "latex", booktabs = "T", caption = cap, 
             align = rep("r", 8)) %>% 
  kableExtra::kable_styling(latex_options = c("hold_position")) %>%
  kableExtra::column_spec(1:3, width = "0.45in") %>%
  kableExtra::column_spec(4:8, width = "0.85in")
```

@@

These results demonstrate our system's ability to create high resolution maps of the distribution and characteristics of cropland across a diverse and hard-to-map agricultural systems, at country-scales and at sub-annual to annual time steps. Our maps provide an updated and more granular view of the distribution and extent of arable croplands in Ghana, complementing existing national to regional land cover maps derived from moderate resolution sensors [@ESAESACCILAND; @hackmanNewLandcoverMaps2017; @XiongNominal30mCropland2017]. These earlier maps estimated that cropland covered `r round(4.62 / 23.86 * 100, 1)` [@XiongNominal30mCropland2017] to 32% [@hackmanNewLandcoverMaps2017] of Ghana's areas in the 2015, in contrast to our maps of cropland in 2018, which cover 16.1-23.2% of the mapped area (Table \href{tab:mapaccuracy}), and yield a sample-corrected estimate `r round(c(42359) / (42359 + 204940) * 100, 1)` to `r round(c(43233) / (43233 + 202856) * 100, 1)`%, which is lower than both prior estimates.

In addition to the more detailed update of cropland extent, our maps also provide new information on the size and number of fields in Ghana (Figures \href{fig:mainmap}, S12). Prior efforts to map such agricultural characteristics have often focused on estimating farm rather than field size using census datasets [@jayneAfricaChangingFarm2016; @LowderNumberSizeDistribution2016; @SambergSubnationaldistributionaverage2016; @VonBraunSmallscalefarmersliberalized2004]. Efforts to map fields in small-scale agricultural systems have either been field-based [@CarlettoFactartifactimpact2013; @CarlettoGuesstimatesGPStimatesLand2015] or remote sensing studies over relatively small areas [e.g. @forkuorIntegrationOpticalSynthetic2014]. The most notable efforts to estimate field sizes were two global initiatives that used crowdsourced volunteers to categorize five broad field size classes based on their interpretations of imagery sampled from virtual globes [@lesivEstimatingGlobalDistribution2019; @FritzMappingglobalcropland2015]. The most recent of these [@lesivEstimatingGlobalDistribution2019] provided country-specific results for Ghana (n = 263) that return an average field size of `r round(lesiv_est, 2)` ha (calculated as the weighted mean of the class counts and the middle values of the four smallest size classes and the lower bound of the largest size class). This estimate exceeds our Ghana-wide average segment size (3.92 ha; Table \href{tab:sizentab}), but is closer to the mean segment size (`r aoi_nofor` ha) across AOIs 1-9, 12, and 15, which is where most of their sample appears to have been collected. However, our bias-corrected estimates of 1.73 (Ghana-wide) and `r aoi_nofor_adj` (AOIs 1-9, 12, and 15) ha are much smaller.

## Sources of error
Although the maps generated by our system provide valuable new information, they nevertheless contain substantial errors. The overall map accuracies are good (86.7-88%, Table \href{tab:mapaccuracy}), which is at the boundary of what could be considered achievable map accuracy [@ElmesAccountingtrainingdata2020], given the level of confidence in the map reference sample (only 85% of reference labels were assigned with confidence). However, accuracies for the cropland class were between 62 (Producer's) and 67 (User's) percent in the per-pixel map, indicating that both commission and omission errors were above 30% for this class. The field boundary has lower omission error (Producer's accuracy = 79%), but that comes at the expense of increased false positives (User's accuracy = 58.2%). These accuracies are near the middle to upper ranges of those reported for the cropland class in other large-area mapping studies [@hackmanNewLandcoverMaps2017; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]

@@

Another major limiting factor was the inherent difficulty of the labelling task. The system is designed to minimize the error inherent in labelling, but determining croplands from non-croplands over these system is difficult and requires educated guessing by each labeller. Interpretation is particularly hard over areas where the background savanna vegetation and croplands have similar reflectance during the dry season, which is a particular problem in AOIs 2 and 3. Such changes in scene circumstances require labellers to adopt different heuristics, for example by delineating the field boundary on the growing season rather than the dry season image. Smaller field sizes also complicated the labelling task, as smaller fields become increasingly indistinct in the ~4 m PlanetScope composites. These challenges caused substantial differences in labels, as evident in the Bayesian Risk metrics (Figure S5) and labeller accuracies that averaged 71%, as measured against our reference set. The design of our system allowed us to measure how much label quality impacts model performance. Although prior work [@mellorExploringIssuesTraining2015; @rodriguez-galianoAssessmentEffectivenessRandom2012] has reported that RandomForest is particularly robust to training data error, we found its impact to be substantial (Figure \href{fig:trainingimpact}), suggesting that the greatest single investment towards improved accuracy lies in improving training data quality.

Image quality was another issue, although primarily in the forest zone (Zone 4) AOIs, where frequent cloud cover reduced the number of available images in all seasons, resulting in composites with more brightness artifacts and blur (Figure \href{fig:imqual}). This impacted labellers' abilities to discern arable fields, and doubtless affected model predictions. There is little to be done to mitigate these errors, short of confining imagery to the less cloudy dry season, which may further undermine model performance--prior work shows that imagery from multiple seasons is important for improving classifier performance [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. Alternatively, composite quality could be improved by integrating imagery from the same seasons over multiple years, but this would undermine the goal of developing annual maps, while the dynamism of the croplands would confound the ability to delineate field boundaries. Alternative compositing approaches might also be ineffective, as the "best-on-top" approach\footnote{https://assets.planet.com/products/basemap/planet-basemaps-product-specifications.pdf} used to develop PlanetScope basemaps tends to result in substantial residual clouds in this region.

The final major error sources relates to the segmentation algorithm, which had two particular problems. The first of these relates to the substantial commission errors in the vector maps, which is attributable to errors in the RandomForest predictions. Uncertainty in that model resulted in substantial numbers of pixels just above the 0.5 classification threshold, meaning a number of segments over highly uncertain areas were retained as fields. This problem would resolve with a more accurate classifier, or potentially by using locally varying thresholds for distinguishing croplands from non-cropland [e.g. @waldnerDeepLearningEdge2020].  The second problem was over-merging by the segmentation algorithm, which caused over-estimation of field sizes and often irregular shapes, particularly in high density croplands, such as in AOIs 2 and 8 (Figure \href{fig:mainmap}), where closely adjacent small-scale fields have boundaries that are often indistinct in the PlanetScope imagery. In this case, minimizing or preventing merging could help, resulting in an over-segmented solution that would likely underestimate field sizes. However, from the standpoint of other map applications, such as filtering pixels for crop type mapping or yield estimation, over-segmented solutions could help by isolating distinct within field units, such as those caused by soil type differences.

## Key system features
- Design of system helped to mitigate these factors:
  - Consensus labels minimize error substantially
  - Active learning selects cites more efficiently, some evidence it improves more efficiently and overall relative to random selection. Less marked gain here, but doing this at much larger scale than Debats
  - Multi-season imagery helps improve it    
    - Feng et al (2020) importance of temporal information (backs up Debats et al).
    - temporal information makes labelling harder though
  - Image quality:

Although the raw maps are biased, data from the labelling platform provides information that can be used to correct for these discrepancies.
The detail, large extent, and temporal precision of the map were enabled by the system's ability to process small-sat data, which currently provide the only wall-to-wall, sub-5 meter imaging capability [@McCabefutureEarthobservation2017] with the frequency necessary to create clean imagery in areas of frequent cloud cover across multiple crop growing periods, which is important for distinguishing cropland from non-cropland [@Debatsgeneralizedcomputervision2016]. This map represents an capability represents an advance over Although free and providing higher radiometric quality and depth, a moderate-resolution sensor such as Sentinel-2 may be too infrequent to successfully penetrate clouds in an area such as southern Ghana (meaning that dry season imagery is likely to be all that is available), while lacking the spatial resolution necessary for labelling and classifying smaller fields.

A possible reason for the discrepancy between earlier maps and ours is that those earlier maps include more areas of active or abandoned cropland in their estimates.

using a mapping system that is designed to work with high spatio-temporal resolution small-sat data.

## Looking forward 
- Provide new insight 
- Given errors, should be considered generation 1 maps
- Sets up capability for repeated annual mapping of croplands to understand critical issues of how these systems are changing (sizes and shapes of croplands, where they are expanding) (Jayne papers, recent agricultural expansion paper)
- Key components will be useful in other applications and regions
- Provides means for improving crop type and crop yield estimates
- Improvements to help realize these capabilities: 
-     [This suggests that replacing the Random Forest more advanced deep learning model]. promise of CNNs (cite Waldner paper, others), for segmentation to realize this. This systems is well designed to adapt to it, and capabilities for assessing various aspects of label quality, e.g. edge accuracy and fragmentation accuracy, can help improve quality of labels designed to emphasize edges
  - Can still retain the active architecture, but instead use new sites to improve a pre-trained model
- Map along agroecozone boundaries, rather than random blocks  
- Another interesting question to answer: whether guided approach to site selection would result in more informative sample for CNNs also.
- Higher number of high quality reference labels can achieve this.

# Suggested uses
- Fallow versus active

- Label quality
  - Accuracy asssessment at training reference sites maybe over-inflated. Each worker saw training reference site multiple times. Need larger number of reference samples
  - Training reference to training ratio was artificially inflated. Workers not always notified when training labels complete, and thus only served training reference sites. 
  - Image-interpreted versus ground labels: **However, these discrepancies are not necessarily an indication of how far workers were from the "truth", but may instead be at least partially an indication of how different the perspectives are as to what constitutes a field when looking at an image versus seeing it from the ground (which in many cases was based on the field team's judgement, rather than farmer guidance).**

Compare values

- The impact of training data error on map quality:
  - Label quality makes a large difference. 
  - Although these comparisons were assessed against consensus-generated validation labels, a visual assessment of probability images generated from each labelling strategy shows markedly greater uncertainty between consensus and most accurate individual labels maps relative to those generated with the lowest quality labels are clearly less certain (Figure S6).

- Left unquantified is how much training on base maps matters

- Assessment of segmentation quality
- Next steps: 
    - Annually updated cropland maps
    - Improvement with deep learning approaches, even with simpler labelling methods [@WangWeaklySupervisedDeep2020]
- Relevant literature: 
    - [@Tongforgottenlanduse2020] discuss Sentinel-based mapping in Sahel, to detect fallows (reference to our intermediate probability values). Semi-automated approach to generating reference data from imagery (based on phenology)
    - [@BeyMappingsmallholderlargescale2020] use CollectEarth to train an algorithm. Multi-stage. No reporting of training or reference data accuracy. 
    - [@LuoDevelopingclearskycloud2008] relevant compositing method to cite, which sounds similar to ours.

>>>>

Based on this reference sample, we found that the overall accuracy of the pixel-wise classifications was 88% (Table \ref{tab:mapaccuracy}). This overall level of accuracy varied within four smaller zones (Figure S9A), ranging from 83.3% in Zone 1 (comprised of AOIs 1-3) to 93.6% in Zone 3 (AOIs 10, 11, 13, 15, and 16). Examining the accuracies of the individual classes, the Producer's accuracy of the cropland class was 61.7% across Ghana, ranging from 45.6% in Zone 3 to 67.9% in Zone 1. The User's accuracy for cropland was 67.3% overall, ranging from 59.8% in Zone 4 to 71.2% in Zone 1. Both measures of accuracy were substantially higher for the non-cropland class across all zones, typically exceeding 90%, with the lowest accuracies for this class found in Zone 1 (Producer's = 89.3% and User's = 87.7%, respectively).

The overall accuracies obtained from the segmented maps were generally 1-2 percentage points lower than those of the per-pixel maps, while User's accuracies tended to be 8-10 percentage points less (Table \ref{tab:mapaccuracy}). In contrast, Producer's accuracies were 15-20 points higher than in the per-pixel map, indicating that the segmentation step helped reduce omission error, but substantially increased false positive errors.

@@

cap <- glue::glue("The average size and total number of crop fields for each ", 
                  "AOI and for Ghana overall. The original and bias-adjusted", 
                  " values for each measure are provided, as well as the total", 
                  " number of 0.05$^\\circ$ degree tiles in each AOI.")
knitr::kable(size_n_tab, format = "latex", booktabs = "T", caption = cap, 
             align = rep("r", 8)) %>% 
  kableExtra::kable_styling(latex_options = c("hold_position")) %>%
  kableExtra::column_spec(1:3, width = "0.45in") %>%
  kableExtra::column_spec(4:8, width = "0.85in")
```

@@

These results demonstrate our system's ability to create high resolution maps of the distribution and characteristics of cropland across a diverse and hard-to-map agricultural systems, at country-scales and at sub-annual to annual time steps. Our maps provide an updated and more granular view of the distribution and extent of arable croplands in Ghana, complementing existing national to regional land cover maps derived from moderate resolution sensors [@ESAESACCILAND; @hackmanNewLandcoverMaps2017; @XiongNominal30mCropland2017]. These earlier maps estimated that cropland covered `r round(4.62 / 23.86 * 100, 1)` [@XiongNominal30mCropland2017] to 32% [@hackmanNewLandcoverMaps2017] of Ghana's areas in the 2015, in contrast to our 2018 maps, in which cropland covers 16.1-23.2% of the mapped area (Table \ref{tab:mapaccuracy}), and yield a sample-corrected estimate `r round(c(42359) / (42359 + 204940) * 100, 1)` to `r round(c(43233) / (43233 + 202856) * 100, 1)`%. This result could suggest that Ghana's arable cropland occupies is less than these previous estimates, or that these previous maps used a more expansive definition of cropland than we used.

In addition to the more detailed update of cropland extent, our maps also provide new information on the size and number of fields in Ghana (Figures \ref{fig:mainmap}, S12). Prior efforts to map such agricultural characteristics have often focused on estimating farm rather than field size using census datasets [@jayneAfricaChangingFarm2016; @LowderNumberSizeDistribution2016; @SambergSubnationaldistributionaverage2016; @VonBraunSmallscalefarmersliberalized2004]. Efforts to map fields in small-scale agricultural systems have either been field-based [@CarlettoFactartifactimpact2013; @CarlettoGuesstimatesGPStimatesLand2015] or remote sensing studies over relatively small areas [e.g. @forkuorIntegrationOpticalSynthetic2014]. The most notable efforts to estimate field sizes were two global initiatives that used crowdsourced volunteers to categorize five broad field size classes based on their interpretations of imagery sampled from virtual globes [@lesivEstimatingGlobalDistribution2019; @FritzMappingglobalcropland2015]. The most recent of these [@lesivEstimatingGlobalDistribution2019] provided country-specific results for Ghana (n = 263) that return an average field size of `r round(lesiv_est, 2)` ha (calculated as the weighted mean of the class counts and the middle values of the four smallest size classes and the lower bound of the largest size class). This estimate exceeds our Ghana-wide average segment size (3.92 ha; Table \ref{tab:sizentab}), but is closer to the mean segment size (`r aoi_nofor` ha) across AOIs 1-9, 12, and 15, which is where most of their sample appears to have been collected. However, our bias-corrected estimates of 1.73 (Ghana-wide) and `r aoi_nofor_adj` (AOIs 1-9, 12, and 15) ha are much smaller.

## Sources of error
Although the maps generated by our system provide valuable new information, they nevertheless contain substantial errors. The overall map accuracies are good (86.7-88%, Table \ref{tab:mapaccuracy}), which is at the boundary of what could be considered achievable map accuracy [@ElmesAccountingtrainingdata2020], given the level of confidence in the map reference sample (only 85% of reference labels were assigned with confidence). However, accuracies for the cropland class were between 62 (Producer's) and 67 (User's) percent in the per-pixel map, indicating that both commission and omission errors were above 30% for this class. The field boundary has lower omission error (Producer's accuracy = 79%), but that comes at the expense of increased false positives (User's accuracy = 58.2%). These accuracies are near the middle to upper ranges of those reported for the cropland class in other large-area mapping studies [@hackmanNewLandcoverMaps2017; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]

@@

Another major limiting factor was the inherent difficulty of the labelling task. Our system was designed to minimize the error inherent in labelling, but determining croplands from non-croplands over these system is difficult and requires the evaluation of multiple image sources and considerable judgement by each labeller. Interpretation is particularly hard over areas where the background savanna vegetation and croplands have similar reflectance during the dry season, which is a particular problem in AOIs 2 and 3. Such changes in scene circumstances require labellers to adopt different heuristics, for example by delineating the field boundary on the growing season rather than the dry season image. Smaller field sizes also complicated the labelling task, becoming increasingly indistinct in the ~4 m PlanetScope composites. The difficulty of labelling is reflected in the magnitude of the Bayesian Risk metrics (Figure S5), and by labeller accuracies that averaged 71% (Figure S4B). The design of our system allowed us to measure how much label quality impacts model performance. Although prior work [@mellorExploringIssuesTraining2015; @rodriguez-galianoAssessmentEffectivenessRandom2012] has reported that RandomForest is particularly robust to training data error, we found its impact to be substantial (Figure \ref{fig:trainingimpact}), suggesting that the greatest single investment towards improved accuracy lies in improving training data quality.

Image quality was another issue, although primarily in the forest zone (Zone 4) AOIs, where frequent cloud cover reduced the number of available images in all seasons, resulting in composites with more brightness artifacts and blur (Figure \ref{fig:imqual}). This impacted labellers' abilities to discern arable fields, and doubtless affected model predictions. There is little to be done to mitigate these errors, short of confining imagery to the less cloudy dry season, which may further undermine model performance--prior work shows that imagery from multiple seasons is important for improving classifier performance [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. Composite quality could be improved by integrating imagery from the same seasons over multiple years, but this would undermine the goal of developing annual maps, while the dynamism of the croplands would confound the ability to delineate field boundaries.

The final major source of error arose from the segmentation process. The vectorized maps had high commission errors that are attributable to the RandomForest predictions. Uncertainty in that model resulted in substantial numbers of pixels just above the 0.5 classification threshold, meaning a number of segments over highly uncertain areas were retained as fields. A more accurate classifier would reduce such errors. Another possible solution could be to apply a locally varying classification threshold to distinguish croplands from non-cropland [e.g. @waldnerDeepLearningEdge2020]. Over-merging was another source of error in the segmentation algorithm. This led in some areas to over-estimation of field sizes and often irregular shapes, particularly in high density croplands (e.g. in AOIs 2 and 8; Figure \ref{fig:mainmap}) where adjacent fields have boundaries that are indistinct in the PlanetScope imagery. Minimizing or preventing merging would help in such cases, although it would result in  over-segmentation and thus would likely underestimate field sizes. However, over-segmentation can help to identify important within-field distinctions (e.g. different soil types), which can be useful for other applications, such as filtering pixels for crop type mapping or yield estimation [e.g. @EstesComparingmechanisticempirical2013; @EstesProjectedclimateimpacts2013]

## Key system features
Despite the sources of errors mentioned above, the design of the system proved effective in mitigating error, resulting in a higher overall accuracy than would have otherwise been possible. The label accuracy assessment and consensus labelling methods appeared to be the most effective tools for error mitigation. Label accuracy assessment allowed us to quantify the impact of trainnig data error on model performance, in keeping with recommended best practices [@ElmesAccountingtrainingdata2020]. Label quality proved to have a large impact on model performance (Figure \ref{fig:trainingimpact}), and consensus labeling was effective in reducing individual digitization errors and between-labeller differences in interpretation, improving label, and thus map, quality. Worker-specific label accuracy measures also helped to improve the overall quality of the consensus labels, by enabling higher weight to be placed on labels that were more likely to be accurate during the merging process, rather than giving equal weight to potentially less accurate labels. The ability to select the most accurate individual labels for a site also allowed us to develop independent estimates of field size to which measures of confidence can be attached (Figure S4B), which we could in turn use to bias-correct map-based size class estimates (Table \ref{tab:sizentab}). The ability to select the most accurate label will also help when different training strategies are needed, such as tasking a model to classify both field edge and interior classes [e.g. @waldnerDeepLearningEdge2020; @aungFarmlandParcelDelineation2020]. In such cases, the vectorized labels are needed to preserve information about the field edges, which are removed during consensus label generation.

```{r, message = FALSE, warning = FALSE, echo=FALSE}
prdelta <- iteration_metrics %>% 
  filter(Metric %in% c("FPR", "TPR")) %>% 
  group_by(Iteration, Metric) %>% 
  summarize(Score = mean(Score)) %>% 
  filter(Iteration %in% c(0, 3)) %>% 
  tidyr::pivot_wider(names_from = Iteration, values_from = Score) %>% 
  mutate(rate = round((`0` - `3`) / `0` * 100, 1))
```
The active learning approach helped to improve overall model performance relative to a randomized approach to training site selection. Although we only compared active to random site selection within three AOIs, the average gains across all three AOIs and three performance metrics demonstrated the effectiveness of the active approach, most notably by the gains in the F1 score (Figure S7), a combined metric of commission and omission error. The gains in accuracy and AUC were smaller. For accuracy, this was due to the larger drop in the active learning metric after iteration 1 in AOI 15, which proved one of the hardest AOIs to map. The plateau in AUC gains at 0.5% relative to random training reflects the fact that each iteration tended to reduce both the false and true positive rates simultaneously. Although the false positive rate overall declined (an average of `r prdelta$rate[1]`% between Iterations 0 and 3), the reductions in true positive rate (averaging `r prdelta$rate[2]`%) offset some of the improved predictive power.

The gain due to active learning were substantially less than those reported by Debats et al (2017), who found that active site selection improved classifier performance by `r round((0.45-0.35) / 0.35 * 100)` over randomized site selection after one iteration, and after 45 iterations by `r round((0.69-0.64) / 0.64 * 100)`%. These larger gains likely reflect the fact that this evaluation began from the smallest possible training sample--one image chip--and tested the effect of adding a single additional chip each iteration. In contrast, we started with a large initial random sample (500) and added 100 samples per iteration, thus our models received significant training at the outset, making the marginal gain due to each new sample smaller. This suggests that we could have benefitted by reducing the size of the initial random training sample while increasing the size of actively selected samples, not only in terms of larger accuracy gains, but also in terms of reducing--by as much as 62%, per Debats et al (2017)--the overall size of the training sample needed to achieve a given level of performance.

The detail, large extent, and temporal precision of the maps we created by virtue of our system's intentional design around PlanetScope imagery, which currently provides the only wall-to-wall, sub-5 meter imaging capability [@McCabefutureEarthobservation2017] with daily frequency. Daily frequency is important for creating multiple seasonal composites during a single agricultural year in cloudy regions. Although unquantified, our compositing technique may be more effective at providing complete image coverage during a season than the "best-on-top" approach\footnote{https://assets.planet.com/products/basemap/planet-basemaps-product-specifications.pdf} used by Planet to develop their analytic basemap, which anecdotally appears to contains substantial residual cloud cover during the growing season in southern Ghana. Although free and providing higher radiometric quality and depth, and of sufficiently high resolution (10 m) to accurately classify small-scale agricultural systems [e.g. @Defournyrealtimeagriculturemonitoring2019; @kernerRapidResponseCrop2020], Sentinel-2's 5-day revist may be too infrequent to provide enough clear pixels to create a cloud-free growing season composite in the southern half of Ghana. Sentinel-1 is not affected by the same problem, but labelling fields in a more coarsely resolved radar images is difficult.

## Lingering questions
Several potential issues not answered by our assessment merit further exploration. These include the correspondence between image- and ground-collected labels. We believe that such comparisons will in most circumstances will reveal unresolvable discrepancies. The highly dynamic nature of the systems in question means that even narrow temporal discrepancies between ground and image-collected labels can produce substantial differences. These discrepancies could be further exacerbated by differences in an understanding of what constitutes a field, which might vary on the ground depending on the farmer or the data collecter's collectors judgement. On top of this, field-collected boundaries are typically highly geographically constrained and limited in size, meaning that any comparison might suggest that the relationship is more noisy than it actually is. These factors suggest that ground versus image label differences would not necessarily indicate how far image-based labellers were from the "truth". Nevertheless, a comparison against ground data can help to assess how accurately image-collected labels capture the typical size of fields, and thus merits further investigation for this reason.

The temporal discrepancies mentioned above [and discussed in @ElmesAccountingtrainingdata2020] are another reason why we chose not to  label on basemap imagery (in addition to restrictive usage terms), which is typically several years old [@LesivCharacterizingspatialtemporal2018]. However, we did not assess whether the higher label accuracy one might achieve by digitizing on <1-2 m basemap would offset model errors due temporal mismatches between labels and imagery.

Another potential issue is the degree to which our assessment of the impact of label error on model performance (Figure \ref{fig:trainingimpacts}) was influenced by the validation labels we used, which were generated using the consensus method. This could have confounded the assessment, particularly when comparing models trained with the most accurate individual label and those trained with consensus labels. However, the visual assessment of probability images generated from each labelling strategy show that these two strategies produce nearly identical maps, and that the model trained with low quality labels generated a markedly less certain map (Figure S6).

## Looking forward 
- Provide new insight 
- Given errors, should be considered generation 1 maps
- Sets up capability for repeated annual mapping of croplands to understand critical issues of how these systems are changing (sizes and shapes of croplands, where they are expanding) (Jayne papers, recent agricultural expansion paper)
- Key components will be useful in other applications and regions
- Provides means for improving crop type and crop yield estimates
- Improvements to help realize these capabilities: 
-     [This suggests that replacing the Random Forest more advanced deep learning model]. promise of CNNs (cite Waldner paper, others), for segmentation to realize this. This systems is well designed to adapt to it, and capabilities for assessing various aspects of label quality, e.g. edge accuracy and fragmentation accuracy, can help improve quality of labels designed to emphasize edges
  - Can still retain the active architecture, but instead use new sites to improve a pre-trained model
  - Deep learning may be more resistant to label errors (cites)
- Map along agroecozone boundaries, rather than random blocks  
- Another interesting question to answer: whether guided approach to site selection would result in more informative sample for CNNs also.
- Higher number of high quality reference labels can achieve this.

- Next steps: 
    - Improvement with deep learning approaches, even with simpler labelling methods [@WangWeaklySupervisedDeep2020]
- Relevant literature: 
    - [@Tongforgottenlanduse2020] discuss Sentinel-based mapping in Sahel, to detect fallows (reference to our intermediate probability values). Semi-automated approach to generating reference data from imagery (based on phenology)
    - [@BeyMappingsmallholderlargescale2020] use CollectEarth to train an algorithm. Multi-stage. No reporting of training or reference data accuracy. 
    - [@LuoDevelopingclearskycloud2008] relevant compositing method to cite, which sounds similar to ours.
